\documentclass{article}
\usepackage{amsmath, amssymb, xpatch, amsthm, outlines}
\usepackage[utf8]{inputenc}

\theoremstyle{plain}

\makeatletter
\xpatchcmd{\@thm}{\thm@headpunct{.}}{}{}

\newtheorem*{def311*}{Definition 3.1.1}
\newtheorem*{def313*}{Definition 3.1.3}
\newtheorem*{def312*}{Definition 3.1.2}

\newtheorem*{lemma311*}{Lemma 3.1.1}

\newtheorem*{theorem311*}{Theorem 3.1.1}
\newtheorem*{theorem312*}{Theorem 3.1.2}
\newtheorem*{theorem313*}{Theorem 3.1.3}
\newtheorem*{theorem314*}{Theorem 3.1.4}

\newtheorem*{lemma312*}{Lemma 3.1.2}

\newtheorem*{definition321*}{Definition 3.2.1}
\newtheorem*{definition322*}{Definition 3.2.2}

\newtheorem*{theorem321*}{Theorem 3.2.1}
\newtheorem*{theorem322*}{Theorem 3.2.2}
\newtheorem*{theorem323*}{Theorem 3.2.3}

\newtheorem*{definition331*}{Definition 3.3.1}
\newtheorem*{definition332*}{Definition 3.3.2}
\newtheorem*{theorem331*}{Theorem 3.3.1}
\newtheorem*{definition333*}{Definition 3.3.3}
\newtheorem*{theorem332*}{Theorem 3.3.2}

\newtheorem*{theorem341*}{Theorem 3.4.1}
\newtheorem*{theorem342*}{Theorem 3.4.2}
\newtheorem*{lemma341*}{Lemma 3.4.1}
\newtheorem*{theorem343*}{Theorem 3.4.3}
\newtheorem*{lemma342*}{Lemma 3.4.2}
\newtheorem*{lemma343*}{Lemma 3.4.3}
\newcommand{\Lagr}{L}
\begin{document}
% \end{document}

$\newline$
\textbf{Definition: Metric Space} Space equipped with a norm $ || \cdot || $. Functions that are elements of the metric space must satisfy the following properties: \vspace{.35 em} \\
1. All functions have positive length save for the zero function. \vspace{.25 em} \\
2. The zero function has zero length. \vspace{.25 em} \\
3. Triangle Inequality: the length of the sum of two functions is always lesser than or equal to the sum of their individual lengths.

$\newline$
Equivalently:
\begin{align*}
& \text{\rm{1. }} \forall f : || f || \geq 0 \\
& \text{\rm{2. }} f = 0 \Leftrightarrow || f || = 0 \\
& \text{\rm{3. }} ||f - g || = || g - f || \\
& \text{\rm{4. }} || f + g || \leq || f || + || g ||
\end{align*}




\section*{The Spaces $L^{p}$}

\subsection*{Measurable Functions}




$\newline$
\textbf{Example 3.1.1 \hspace{.5 em} The Vitali Set $ V $}

\begin{def311*} \text{\rm{\textbf{Measurable Function}}}
\end{def311*}

%$\newline$
\begin{theorem311*} \end{theorem311*}

%$\newline$
\begin{theorem312*} Assume f is measurable, and let $ g $ be a Lebesgue integrable function. If $ |f| \leq g $, then $ f $ is Lebesgue integrable. Furthermore, if $ | f | $ is Lebesgue integrable, then $ f $ is too.
\end{theorem312*}

\subsection*{Definition of $L^{p}$ Spaces}

%$\newline$
\begin{theorem313*} On an $L^{p}$ space with $ p \geq 1 $,
\end{theorem313*}

%$\newline$
\begin{def312*} \text{\rm{\textbf{$L^{p}$ Function Space}}}
\end{def312*}

%$\newline$
\begin{lemma311*} \text{\rm{\textbf{Hölder's Inequality}}} \\
Assume $ p, q > 1 $ satisfy $ \frac{1}{p} + \frac{1}{q} = 1 $. Then:
$$ \forall f, g : f \in L^{p} \hspace{.1 em} \land \hspace{.1 em} g \in L^{q} \hspace{.125 em} \implies \hspace{.125 em} f \cdot g \in L^{1} \hspace{.1 em} \land \hspace{.1 em} \int | f \cdot g | \leq || f ||_{p} \cdot || g ||_{q}
$$
\end{lemma311*}



\subsection*{Completeness of $ L^{p} $ Spaces}
\begin{def313*} \text{\rm{\textbf{Convergence of $ L^{p} $ Functions}}}
\end{def313*}

\begin{lemma312*} \end{lemma312*}


\begin{theorem314*} \text{\rm{\textbf{The Riesz-Fischer Theorem}}}
\end{theorem314*}

 

\section*{$L^{2}$ and $\ell^{2} $ Hilbert Space Properties}

\begin{definition321*} \text{\rm{\textbf{Inner Product of}}} $L^{2}\left(\mathbb{R}\right)$ \text{\rm{\textbf{Functions}}}
\end{definition321*}


\begin{theorem321*} \text{\rm{\textbf{The Schwarz Inequality}}}
\end{theorem321*}

\begin{theorem322*} \text{\rm{\textbf{The Pythagorean Theorem}}}
\end{theorem322*}

\begin{theorem323*} \text{\rm{\textbf{The Parallelogram Law}}}
\end{theorem323*}

\begin{definition322*} \text{\rm{\textbf{Inner Product of}}} $L^{2}\left(a,b\right)$ \text{\rm{\textbf{functions}}} \\
\end{definition322*}

\section*{Hilbert Space Orthonormal Basis}

\textbf{Definition: Hilbert Space} \\
A normed, linear, inner product space. \\
Possess properties of Euclidean space which allow for application of calculus.

\subsection*{Vector Space Basis}

\begin{theorem331*} \text{\rm{\textbf{Orthogonal Basis for Hilbert Space}}}
\end{theorem331*}

\subsection*{Gram-Schmidt Process}

%\begin{definition332*} \text{\rm{\textbf{The Gram-Schmidt Process}}}
%\end{definition322*}

\begin{definition332*} \text{\rm{\textbf{The Gram\--Schmidt Process}}}
\end{definition332*}


\subsection*{The Projection Theorem}

\begin{theorem331*} \text{\rm{\textbf{Basis Approximation Theorem}}} \\
\end{theorem331*}

\subsection*{Equivalence of Hilbert Spaces}

\begin{definition333*} \text{\rm{\textbf{Hilbert Space Isomorphism}}}
\end{definition333*}

\begin{theorem332*}
\end{theorem332*}

\section*{Application: Quantum Mechanics}
\subsection*{The Hermite Differential Equation}
\subsection*{The Hermite Functions Form an Orthogonal Basis for $ L^{2}\left(\mathbb{R}\right) $}



















































































\end{document}